EPQ Trapdoor Function

### 2017-06-21 latex/qtpie/paper.tex
improved signaturetest

\section{Introduction}
A Trapdoor One-Way Function (TOWF) is a function that is easy to compute in one direction, but is hard to compute in reverse without some additional piece of information. A TOWF makes exchanging cryptographic keys a straightforward exercise: Alice can simply apply a TOWF to a randomly generated key and send the output to Bob, who knows the trapdoor information. Bob can then invert the output to obtain the key.

In this paper we define a candidate Trapdoor One-Way Function that is suitable for use to exchange cryptographic keys. It is based on a simple observation of a congruence, $pq + e \equiv q + p_i e \mod N$, along with some subtle manipulation of the sizes of the numbers involved.

@@

\section{Algorithm}
There is a publicly agreed upon modulus $N$. The same $N$ may always be used. It must be prime; It it is not secret, and otherwise only needs to be both agreed upon and large enough. The size of $N$ is determined by the rest of the parameter sizes which are discussed below; In our python implementation, $N$ is slightly less then 800 bits in size. The larger $N$ is, the longer the BigNum arithmetic operations take, and the larger ciphertexts become; Consequently, we opt for the smallest $N$ possible.

@@

The step $q := t \mod p_i$ will only function correctly if $q < p_i$ and if $p_i e < N$. We leverage this latter fact to create a trapdoor. We select a suitable $p_i$ that is large enough such that $q < p_i$ and small enough such that $p_i e < N$. Then, we calculate the modular multilicative inverse $p := inverse(p_i, N)$. To create a public key, we then encrypt $p$ using a random $r$ to preclude the ability of others to calculate $p_i$.

The inability to selectively generate a small inverse of the public key ensures that supplying the public key to the inversion algorithm will not produce correct plaintext. We can witness this via the attempt below:

@@

@@

This implies that the private key cannot be recovered from the public key.

@@

\section{Conclusion}
We define a conceptually simple, resource-practical key exchange algorithm. 
\end{document}

>>>>

\section{Introduction}
A Trapdoor One-Way Function (TOWF) is a function that is easy to compute in one direction, but is hard to compute in reverse without some additional piece of information. A TOWF makes exchanging cryptographic keys a straightforward exercise: Alice can simply apply a TOWF to a randomly generated key and send the output to Bob, who knows the trapdoor information. Bob can then use the trapdoor information to invert the output and obtain the key.

In this paper we define a candidate TOWF that is suitable for use to exchange cryptographic keys. It is based on a simple observation of a congruence, $pq + e \equiv q + p_i e \mod N$, along with some subtle manipulation of the sizes of the numbers involved.

@@

\section{Algorithm}
There is a publicly agreed upon modulus $N$. The same $N$ may always be used. It must be prime; It it is not secret, and otherwise only needs to be both agreed upon and large enough. The size of $N$ is determined by the rest of the parameter sizes which are discussed below; In our python implementation which targets a 256-bit security level, $N$ is slightly less then 800 bits in size. The larger $N$ is, the longer the BigNum arithmetic operations take, and the larger ciphertexts become; Consequently, we opt for the smallest $N$ possible.

@@

The step $q := t \mod p_i$ will only function correctly if $q < p_i$ and if $p_i e < N$. We leverage this latter fact to create a trapdoor. We select a suitable $p_i$ that is large enough such that $q < p_i$ and small enough such that $p_i e < N$. Then, we calculate the modular multilicative inverse $p := inverse(p_i, N)$. This number will likely be very large, closer to $N$ in size then to $p_i$. To create a public key, we then encrypt $p$ using a random $r$ to preclude the ability of others to calculate $p_i$.

The public key provides the ability to compute the forward operation $p q + e \mod N$ because there is no size constraint on $p$ for this operation (as long as $p < N$ anyways). Supplying the inverse of the public key to the inversion algorithm will not produce correct plaintext, because the generated value will be too large. We can witness this via the attempt below:

@@

\subsubsection{$q$ and Anti-Malleability}
If $q$ is used as the secret instead of $e$, then the ability to add plaintext values to ciphertexts disappears. The value of $e$ will not influence $q$, and manipulations of the ciphertext less then a certain magnitude will not modify the plaintext obtained upon decryption. This is in stark contrast to the more common Non-Malleability, where modification of the ciphertext will usually modify the corresponding plaintext to a meaningless value.

@@

This implies that there does not exist an algorithm to recover the private key from the public key, other then brute force guessing.

@@

\section{Conclusion}
We define a conceptually simple, resource-practical Trapdoor One-Way Function and key exchange algorithm. 
\end{document}
